### 2020-12-11 paper/localpsf.tex
wrote weighting function algorithm at infinite dimensional level

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to following Poisson problem with pure Neumann boundary conditions and a point source at $x_i$:
			$$\begin{cases}
			\Delta \psi_i = \delta_{x_i}, & \text{in }\Omega,\\
			\nu \cdot \nabla \psi_i = 0, & \text{on }\partial \Omega,\\
			\int_\Omega \psi_i(x) dx = 0.
			\end{cases}$$

			Compute $\theta_i$ as the solution to the following Poisson problem with pure Neumann boundary conditions and source $\psi_i$:
			$$\begin{cases}
			\Delta \theta_i = \psi_i, & \text{in }\Omega,\\
			\nu \cdot \nabla \theta_i = 0, & \text{on }\partial \Omega,\\
			\int_\Omega \theta_i(x) dx = 0.
			\end{cases}$$
		}

@@

			Compute
			$$w_i = -\sum_{k=1}^r \lambda_k \theta_k + \alpha C,$$
			where we recall that $C$ is the constant function $C(x)=1$ on $\Omega$.
		}
	}
	\caption{Compute weighting functions $w_i$, $i=1,\dots,r$.}
	\label{alg:weighting_functions_incremental}
\end{algorithm2e}

>>>>

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to the Poisson problem
			\begin{equation*}
				\Delta \psi_i = \delta_{x_i}, \quad \text{in }\Omega,
			\end{equation*}
			with Neumann boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

			Compute $\theta_i$ as the solution to the Poisson problem
			\begin{equation*}
			\Delta \theta_i = \psi_i, \quad \text{in }\Omega,
			\end{equation*}
			with Neumann boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

@@

			Form the weighting function
			$$w_i = -\sum_{k=1}^r \lambda_k \theta_k + \alpha C,$$
			where we recall that $C$ is the constant function $C(x)=1$ on $\Omega$.
		}
	}
	\caption{Compute weighting functions $w_i$, $i=1,\dots,r$.}
	\label{alg:weighting_functions_incremental}
\end{algorithm2e}
